Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-01-28 msc-publication.tex
more introduction
add ametsoc style and a bibtex reference

\documentclass[a4paper]{article}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{siunitx}
\usepackage{booktabs}

\title{Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model}
\author{James Shaw}
\date{TODO}

@@

Builds on the work of \textcite{schaer2002} (MWR), \textcite{klemp2011} (MWR), \textcite{weller-shahrokhi2014} (MWR)

@@

\begin{itemize}
	\item Comparing results BTF, SLEVE and cut cell style grid for three standard two-dimensional test cases
	\item Small cell problem
\end{itemize}

@@

\begin{table}
\centering
\begin{tabular}{ l l l l l l }
\toprule
& \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{2}{c}{Sch\"ar 4th order} \\
& $\ell^2$ error & min & max & min & max \\
\midrule
Analytic  & 0 & 0 & 1 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
BTF 	  & TODO & TODO & TODO & \num{-0.058} & \num{1.001} \\
SnapCol   & TODO & TODO & TODO & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
noOrography & TODO & TODO & TODO & \num{-0.002} & \num{0.984} \\
\bottomrule
\end{tabular}
%
\caption{Min, max and error norms compared with \textcite{schaer2002}}
\label{tab:advection}
\end{table}

@@

\section{Further work}
\begin{itemize}
	\item Lorenz computational mode motivates formulation of C-P staggering for cut cell grids
	\item Find out what excites the Lorenz computational mode
\end{itemize}

>>>>

\documentclass{ametsoc}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{siunitx}

\bibpunct{(}{)}{;}{a}{}{,}

\title{Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model}
\authors{James Shaw\correspondingauthor{Dept., Institution, Address, City, State/Country.}}
\affiliation{}
\email{j.shaw@pgr.reading.ac.uk}

\abstract{Enter the text of your abstract here.}

@@

Builds on the work of \citet{schaer2002} (MWR), \textcite{klemp2011} (MWR), \textcite{weller-shahrokhi2014} (MWR)

@@

\begin{itemize}
	\item Comparing results BTF, SLEVE and cut cell style grid for three standard two-dimensional test cases
	\item TF grids often shown to have lesser accuracy than cut cells in some test cases, often significantly so.  Our results demonstrate that accuracy need not be much reduced and can even be better than cut cells.
	\item Small cell problem common in cut cell grids (\TODO{citations})
\end{itemize}

@@

@@

\section{Further work}
\begin{itemize}
	\item Lorenz computational mode motivates formulation of C-P staggering for cut cell grids
	\item Find out what excites the Lorenz computational mode
	\item \TODO{anything else?}
\end{itemize}

\acknowledgments
Start acknowledgments here.

% REFERENCES

\bibliographystyle{ametsoc2014}
\bibliography{references}

% TABLES

\begin{table}[t]
\caption{Min, max and error norms compared with \textcite{schaer2002}}
\label{tab:advection}
%
\begin{center}
\begin{tabular}{ l l l l l l }
\hline\hline
& \multicolumn{3}{c}{Cubic upwind-biased} & \multicolumn{2}{c}{Sch\"ar 4th order} \\
& $\ell^2$ error & min & max & min & max \\
\hline
Analytic  & 0 & 0 & 1 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
BTF 	  & TODO & TODO & TODO & \num{-0.058} & \num{1.001} \\
SnapCol   & TODO & TODO & TODO & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\
noOrography & TODO & TODO & TODO & \num{-0.002} & \num{0.984} \\
\hline
\end{tabular}
\end{center}
\end{table}

% FIGURES
